---
title: "Homework 1"
output: 
  pdf_document: 
    latex_engine: xelatex
header-includes:
- \usepackage{xeCJK}
---
```{r setup, message = F, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(DAAG)
```
1. The Iowa data set iowa.csv is a toy example that summarises the yield of wheat (bushels per acre) for the state of Iowa between 1930-1962. In addition to yield, year, rainfall and temperature were recorded as the main predictors of yield.
    a. First, we need to load the data set into R using the command `read.csv()`. Use the help function to learn what arguments this function takes. Once you have the necessary input, load the data set into R and make it a data frame called `iowa.df`.
```{r}
iowa.df<-read.csv("C:/Users/lenovo/Documents/github/Rcourse2020/data/Iowa.csv", header=T, sep=";")
```
b. How many rows and columns does `iowa.df` have? 
```{r}
nrow(iowa.df)
ncol(iowa.df)
```
c. What are the names of the columns of `iowa.df`?
```{r}
colnames(iowa.df)
```
d. What is the value of row 5, column 7 of `iowa.df`?
```{r}
iowa.df[5,7]
```
e. Display the second row of `iowa.df` in its entirety.
```{r}
iowa.df[2,]
```

2. Syntax and class-typing.
    a. For each of the following commands, either explain why they should be errors, or explain the non-erroneous result.
```{r eval=FALSE}
vector1 <- c("5", "12", "7", "32")
max(vector1)
sort(vector1)
sum(vector1)
```
max(vector1): [1] "7"

sort(vector1): [1] "12" "32" "5"  "7" 

Error in sum(vector1) : 'type'(character)参数不对。

sum（vector1）运行错误，因为sum（）的第一个参数必须是数字，复数或逻辑向量，但是vector1是字符向量。

b. For the next series of commands, either explain their results, or why they should produce errors.

```{r eval=FALSE}
vector2 <- c("5",7,12)
vector2[2] + vector2[3]
dataframe3 <- data.frame(z1="5",z2=7,z3=12)
dataframe3[1,2] + dataframe3[1,3]
list4 <- list(z1="6", z2=42, z3="49", z4=126)
list4[[2]]+list4[[4]]
list4[2]+list4[4]
```
vector2[2] + vector2[3]:
Error in vector2[2] + vector2[3]:二进列运算符中有非数值参数

vector2[2] + vector2[3]运行错误，因为vector中的值是同类型的，第一个值是字符类型的所以后面两个值也会转化为字符类型。字符类型的两个值不能相加。

dataframe3[1,2] + dataframe3[1,3]:
dataframe中的值允许各种类型，所以不会存在上面vector的问题。

list4[[2]]+list4[[4]]:list4[[2]]=42, list4[[4]]=126,可以相加，结果为168。

list4[2]+list4[4]:list4[2]和list[4]均为vector，不可相加。

3. Working with functions and operators.
    a. The colon operator will create a sequence of integers in order. It is a special case of the function `seq()` which you saw earlier in this assignment. Using the help command `?seq` to learn about the function, design an expression that will give you the sequence of numbers from 1 to 10000 in increments of 372. Design another that will give you a sequence between 1 and 10000 that is exactly 50 numbers in length.
```{r}
seq(1,10000,372)
seq(1,10000,length.out = 50)
```
b. The function `rep()` repeats a vector some number of times. Explain the difference between `rep(1:3, times=3) and rep(1:3, each=3).
```{r}
rep(1:3, times=3)
rep(1:3, each=3)
```
差别：times的值表示整个向量重复几次，而each的值表示向量中的每个元素重复几次。

MB.Ch1.2. The orings data frame gives data on the damage that had occurred in US space shuttle launches prior to the disastrous Challenger launch of 28 January 1986. The observations in rows 1, 2, 4, 11, 13, and 18 were included in the pre-launch charts used in deciding whether to proceed with the launch, while remaining rows were omitted.

Create a new data frame by extracting these rows from orings, and plot total incidents against temperature for this new data frame. Obtain a similar plot for the full data set.
```{r}
orings.sample<-orings[c(1,2,4,11,13,18),]
ggplot(orings.sample)+
  geom_point(aes(x=Temperature,y=Total))+
  ggtitle("Sample")
ggplot(orings)+
  geom_point(aes(x=Temperature,y=Total))+
  ggtitle("Total")
```
MB.Ch1.4. For the data frame ais (DAAG package)

(a) Use the function str() to get information on each of the columns. Determine whether any of the columns hold missing values.
```{r}
str(ais)
```
经观察，没有列有缺失数据。

(b) Make a table that shows the numbers of males and females for each different sport. In which sports is there a large imbalance (e.g., by a factor of more than 2:1) in the numbers of the two sexes?
```{r}
ais[,c("sex","sport")] %>% group_by(sport,sex) %>% summarise(number=n())
```
观察发现T_sprnt的男女比例不均衡，男比女等于11:4>2:1。

MB.Ch1.6.Create a data frame called Manitoba.lakes that contains the lake’s elevation (in meters above sea level) and area (in square kilometers) as listed below. Assign the names of the lakes using the row.names() function.
               elevation  area
Winnipeg             217 24387
Winnipegosis         254  5374
Manitoba             248  4624
SouthernIndian       254  2247
Cedar                253  1353
Island               227  1223
Gods                 178  1151
Cross                207   755
Playgreen            217   657
```{r}
a.matrix<-matrix(c(217,24387,254,5374,248,4624,254,2247,253,1353,227,1223,178,1151,207,755,217,657),ncol = 2,byrow = TRUE)
Manitoba.lakes<-data.frame(a.matrix)
row.names(Manitoba.lakes)<-c("Winnipeg","Winnipegosis","Manitoba","SouthernIndian","Cedar","Island","Gods","Cross","Playgreen")
colnames(Manitoba.lakes)<-c("elevation","area")
```

(a) Use the following code to plot log2(area) versus elevation, adding labeling information (there is an extreme value of area that makes a logarithmic scale pretty much essential):
```{r}
attach(Manitoba.lakes)
plot(log2(area) ~ elevation, pch=16, xlim=c(170,280))
# NB: Doubling the area increases log2(area) by 1.0
text(log2(area) ~ elevation, labels=row.names(Manitoba.lakes), pos=4)
text(log2(area) ~ elevation, labels=area, pos=2) 
title("Manitoba’s Largest Lakes")
```
Devise captions that explain the labeling on the points and on the y-axis. It will be necessary to explain how distances on the scale relate to changes in area.

(b) Repeat the plot and associated labeling, now plotting area versus elevation, but specifying log="y" in order to obtain a logarithmic y-scale.
```{r}
plot(area ~ elevation, pch=16, xlim=c(170,280), log="y")
text(area ~ elevation, labels=row.names(Manitoba.lakes), pos=4, ylog=T)
text(area ~ elevation, labels=area, pos=2, ylog=T) 
title("Manitoba’s Largest Lakes")

```
MB.Ch1.7. Look up the help page for the R function dotchart(). Use this function to display the areas of the Manitoba lakes (a) on a linear scale, and (b) on a logarithmic scale. Add, in each case, suitable labeling information.
```{r}
dotchart(area,labels=row.names(Manitoba.lakes))
dotchart(log2(area),labels=row.names(Manitoba.lakes))
```

MB.Ch1.8. Using the sum() function, obtain a lower bound for the area of Manitoba covered by water.
```{r}
sum(Manitoba.lakes[,"area"])
```

