---
title: 'Lab 3: Data Wrangling on Soccer Tournament Data'
date: 'July 9, 2020'
output:
  pdf_document: default
  html_document: default
---
```{r setup, message = F, include=FALSE}
library(tidyverse)
```

Soccer tournament data wrangling
--------------------------
Read the dataset of football games.
```{r}
d <- read_csv("../data/results.csv")
```

1. Select variables `date`, `home_team` and `away_team`.
```{r}
select(d,date,home_team,away_team)
```
2. Subset games with **Brazil** as the home team.
```{r}
filter(d, home_team=="Brazil")
```

3. Choose the games that Brazil won as the home team, and select variables `date`, `away_team` and `tournament`.
```{r}
filter(d, home_team=='Brazil', home_score>away_score) %>% 
  select(date,away_team,tournament)
```

4. Add the difference of goals, and an indicator variable called `goleada` for when the difference of goals is large,  and select what we did only for Brazil. **Hint: use `ifelse`**.
```{r}
d1 <- d %>% mutate(diff_goal=abs(home_score-away_score)) %>% mutate(goleada=if_else(diff_goal > 3, "True", 'False')) %>% 
  filter(home_team == 'Brazil' | away_team == 'Brazil', goleada == 'True')
d1
```

5. What was the largest difference in goals within these games?
```{r}
max(d1[,10])
```

6. The top 5 goleadas?
```{r}
arrange(d1,desc(diff_goal)) %>% head(5)
```
7. Summary on goals scored by home teams, such as `mean` of `home_score` and `away_score`, `std`, using `group_by` and `summarise`
```{r}
d %>% 
  group_by(home_team) %>% 
  summarize(meanhome=mean(home_score),meanaway=mean(away_score),std=sd(home_score))
```

8. Proportion of victories of **Brazil** on different tournaments against each opponent, for instance, **Argentina**.
```{r}
v1 <- d %>% 
  filter(home_team == 'Brazil') %>% 
  mutate(result=if_else(home_score - away_score > 0, TRUE, FALSE)) %>% 
  group_by(away_team) %>% 
  summarise(victories = sum(result), games = n())
v2 <- d %>% 
  filter(away_team == 'Brazil') %>% 
  mutate(result=if_else(away_score - home_score > 0, TRUE, FALSE)) %>% 
  group_by(home_team) %>% 
  summarise(victories = sum(result), games = n())
colnames(v1) <- c('team','victories_home','games_home')
colnames(v2) <- c('team','victories_away','games_away')
v <- inner_join(v1,v2,by = "team") %>% 
  mutate(vicory_proportion = (victories_home+victories_away)/(games_home+games_away))
v
```
